---
title: "Y1H"
output: html_document
---
<h2>Purpose and data explanation</h2>



The purpose of this is to create a simple way to turn the data of a Yeast one-hybrid experiment into easily understandable results. These results can be gotten from the manipulation of certain variables that will control the sensitivity of the data.

Our data is broken up into promoters, as shown in the following figure. <https://goo.gl/2KVAPz>

<h4>A and B do not signify order, just that they are different genes</h4>

The promoters are labeled pIAAX - A, pIAAX - B, and, in some cases, pIAAX - C.

A, B, and C denote a portion of a gene but doesn't necessarily indicate which segment of the gene - only that it is a different part.

X is a number that denotes the bait ID number.


---

<h3>Key</h3>

<table style="width:100%">
  <tr>
    Column             Column Name         Discription
      A                 AGI                 TF gene ID number
      B                 Family              gene family
      C                 LUM                 Luminescence value
      D                 OD600               Cell growth = the optical density at 600nm
      E                 Cell.vol            volume of cells in mL, This data has all = .025
      F                 Time                This data has time of reaction = 1
    
</table>

<h3>Step 1: Formatting</h3>

The first thing that I did was to format each Excel document to contain a single header and the following data:
AGI, Family, Lum, OD600, cell vol, time


I deleted the following information from the excel so that we can set them as variables throughout the rest of the R script:
Bait ID, OD600 cutoff value, AVR LUM control, AVR-LUM_bkg, AVR-OD600_bkg, SD-OD600_bkg, AVR-LUM_ctrl, SD_LUM_ctrl, Fold_Ind_C.O., the number of High confidence interactions,

I deleted the following columns:
Plate-well, DNAarray, blank, Lum_bkg, Lum-bkg, bkg600, od600-b, well, AVRplate, AVRall, plate and all, control vs Control (per plate), and the conclusion.

The final formatting in Excel looks like this <https://gyazo.com/e544915e58fe3c00894904cf4f9fbdea>

Each Excel sheet was saved as a CSV file so that RStudio can import it.

---
<h3>Step 2: Importing Data set</h3>

The following code will allow you to import and view the CSVs from your working directory as long as they are properly directed.

It will also change any blank values within the Excel document to an NA value.

It will also clean the data frame by removing any row that has an NA in it.

However, I am coming across a problem that I have an extra column (column "x"). So I will have to manually drop that column.



```{r}
IAA1...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA1 - A.csv", na.strings = c("","NA"))
IAA1...A$X <- NULL ##Drop the extra column
Clean_IAA1...A <- na.omit(IAA1...A) #Removes any row with an NA value
View(IAA1...A)
```

---

<h3>Step 3: Removing Low Values</h3>


The following code will create a subset of the imported data that is greater than or equal to the indicated variable, which removes the values that are lower than the indicated value.

"growth" indicates the cutoff point where all other data will be excluded from calculations.

"Refined_1A" is the new set of data that is greater than or equal to the growth variable. The reason I chose to name them XA or XB or XC is because we will start to have a large amount of these functions and it is good to name them an appropriate name before having 30 of them to sift through.

The data set IAA1...A is our previously imported data set.

OD600 is a header within the data set.


```{r}

growth <- .2 ##Change this to change the minimum value of OD600

Refined_1A <- subset(Clean_IAA1...A, OD600 >= growth)


```

---

<h3>Step 4: Analyzing Results</h3>

After completing steps 1 through 3 on each set of data, I began to analyze the results.

I wasn't exactly sure what to look at, but this is the basics of it.

```{r}

plot(Refined_1A$Lum,Refined_1A$OD600) ##This plots the Lum (x-axis) vs OD600 (y-axis)

```
---


<h2>Questions</h2>


<h4>Question 1</h4>
So, I manually inputted each one in like so. I was wondering if it was possible to automate that process? It was very time consuming even when copying and pasting, I had to change IAA1...A to IAA1...B and so forth. I also had to change WD/IAA1 - A to WD/IAA1 - B. All in all, this was the longest part of the entire thing.

Is it possible to automatically generate a funciton based on a pattern?

```{r}

IAA1...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA1 - A.csv", na.strings = c("","NA"))
IAA1...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA1 - B.csv", na.strings = c("","NA"))
IAA3...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA3 - A.csv", na.strings = c("","NA"))
IAA3...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA3 - B.csv", na.strings = c("","NA"))
IAA5...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA5 - A.csv", na.strings = c("","NA"))
IAA5...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA5 - B.csv", na.strings = c("","NA"))
IAA6...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA6 - A.csv", na.strings = c("","NA"))
IAA6...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA6 - B.csv", na.strings = c("","NA"))
IAA6...C <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA6 - C.csv", na.strings = c("","NA"))
IAA7...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA7 - A.csv", na.strings = c("","NA"))
IAA7...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA7 - B.csv", na.strings = c("","NA"))
IAA9...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA9 - A.csv", na.strings = c("","NA"))
IAA9...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA9 - B.csv", na.strings = c("","NA"))
IAA10...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA10 - A.csv", na.strings = c("","NA"))
IAA10...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA10 - B.csv", na.strings = c("","NA"))
IAA12...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA12 - A.csv", na.strings = c("","NA"))
IAA12...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA12 - B.csv", na.strings = c("","NA"))
IAA14...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA14 - A.csv", na.strings = c("","NA"))
IAA14...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA14 - B.csv", na.strings = c("","NA"))
IAA15...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA15 - A.csv", na.strings = c("","NA"))
IAA15...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA15 - B.csv", na.strings = c("","NA"))
IAA17...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA17 - A.csv", na.strings = c("","NA"))
IAA17...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA17 - B.csv", na.strings = c("","NA"))
IAA26...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA26 - A.csv", na.strings = c("","NA"))
IAA26...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA26 - B.csv", na.strings = c("","NA"))
IAA30...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA30 - A.csv", na.strings = c("","NA"))
IAA30...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA30 - B.csv", na.strings = c("","NA"))
IAA33...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA33 - A.csv", na.strings = c("","NA"))
IAA33...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA33 - B.csv", na.strings = c("","NA"))
IAA34...A <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA34 - A.csv", na.strings = c("","NA"))
IAA34...B <- read.csv("D:/Documents/College/Research/Y1H/Updated pIAA CSVs and WD/IAA34 - B.csv", na.strings = c("","NA"))

```

---
<h4>Question 2</h4>

Another automating question.

When changing the variable "growth" is it possible to have the funcitons Refined_XA update? I have to paste them into the console to have them update, which is time consuming.

```{r}

growth <- .25 ##Change this to change the minimum value of OD600

Refined_1A <- subset(Clean_IAA1...A, OD600 >= growth)
Refined_1B <- subset(Clean_IAA1...B, OD600 >= growth)
Refined_3A <- subset(Clean_IAA3...A, OD600 >= growth)
Refined_3B <- subset(Clean_IAA3...B, OD600 >= growth)
Refined_5A <- subset(Clean_IAA5...A, OD600 >= growth)
Refined_5B <- subset(Clean_IAA5...B, OD600 >= growth)
Refined_6A <- subset(Clean_IAA6...A, OD600 >= growth)
Refined_6B <- subset(Clean_IAA6...B, OD600 >= growth)
Refined_6C <- subset(Clean_IAA6...C, OD600 >= growth)
Refined_7A <- subset(Clean_IAA7...A, OD600 >= growth)
Refined_7B <- subset(Clean_IAA7...B, OD600 >= growth)
Refined_9A <- subset(Clean_IAA9...A, OD600 >= growth)
Refined_9B <- subset(Clean_IAA9...B, OD600 >= growth)
Refined_10A <- subset(Clean_IAA10...A, OD600 >= growth)
Refined_10B <- subset(Clean_IAA10...B, OD600 >= growth)
Refined_12A <- subset(Clean_IAA12...A, OD600 >= growth)
Refined_12B <- subset(Clean_IAA12...B, OD600 >= growth)
Refined_14A <- subset(Clean_IAA14...A, OD600 >= growth)
Refined_14B <- subset(Clean_IAA14...B, OD600 >= growth)
Refined_15A <- subset(Clean_IAA15...A, OD600 >= growth)
Refined_15B <- subset(Clean_IAA15...B, OD600 >= growth)
Refined_17A <- subset(Clean_IAA17...A, OD600 >= growth)
Refined_17B <- subset(Clean_IAA17...B, OD600 >= growth)
Refined_26A <- subset(Clean_IAA26...A, OD600 >= growth)
Refined_26B <- subset(Clean_IAA26...B, OD600 >= growth)
Refined_30A <- subset(Clean_IAA30...A, OD600 >= growth)
Refined_30B <- subset(Clean_IAA30...B, OD600 >= growth)
Refined_33A <- subset(Clean_IAA33...A, OD600 >= growth)
Refined_33B <- subset(Clean_IAA33...B, OD600 >= growth)
Refined_34A <- subset(Clean_IAA34...A, OD600 >= growth)
Refined_34B <- subset(Clean_IAA34...B, OD600 >= growth)

```